On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-08 3_Method.tex
ajustes nas issues apontadas por Marcio

\begin{enumerate}[(RQ1)]
    \item Do JavaScript developers identify atoms of confusion as contributing to program misunderstanding? 
    \item What is the impact of atoms of confusion on the comprehension of JavaScript code? 
    \item What are the particular JavaScript idioms and language constructs that might cause source code misunderstanding?
    \item What is the frequency of occurrence of atoms of confusion in practice (i.e., in open-source JavaScript projects)?
\end{enumerate}

@@

In the first study we explore the impact of atom candidates on
understanding JavaScript code, by answering two questions:
(a) \emph{Do code snippets that contain atom candidates
produce a higher misunderstanding rate when programmers
try to predict their outcome?}
and (b) \emph{Do code snippets with atom candidates require
programmers to take longer to predict their output?}
Since JavaScript and C have some constructs in common (Section~\ref{sec:aoc}), we first selected a set of atoms of confusion for the \clang language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} whose idioms also exist in JavaScript programs. Our supplementary material
summarizes all atoms we consider in our research.

@@

Having selected 10 atoms in our first study, we wrote small pieces of code that contained each atom. We also wrote their equivalent snippet without the confusing idioms and constructs, leading to a total of 20 code snippets. In order to reduce the cognitive effort, we decided that each subject would be asked to predict the output of a subset of 10 code snippets, wherein each subset contained 5 blocks of code that contained atoms of confusion, whilst the remaining 5 had the atoms removed. The order in which the questions were presented was randomized. By doing this, we were seeking to minimize the chances of subjects being aware that the current listing they were analyzing contained (or not) atoms of confusion.
That is, each respondent of the survey should indicate what would be the outcomes of the code snippets, some of them having atoms of confusion (while other code snippets did not). 
We measured answer correctness and the total time each participant needed to answer the survey's questions.

@@

To complement our initial survey, we performed semi-structured interviews with professional JavaScript developers, aiming to identify their perceptions regarding code snippets containing atoms of confusion. We also asked each participant if they knew of any other JavaScript-specific construct that they regarded as being likely to make the code hard to understand. In this section we detail the protocol we followed to conduct the interviews and to analyze the results.

@@

In the second part of the interview our aim was to allow the subjects to describe
their JavaScript experience, as well as to allow them to reveal any JavaScript's constructs they regarded as innately confusing. This would allow us to identify potential atom candidates that are more specific to the JavaScript language. Examples of questions we explored in this section include:\emph{Do you think JavaScript is a language that produces code that is hard to understand?} and \emph{Do you regard any particular construct or idiom of the language as
  especially confusing?}

@@

After filtering out JavaScript project candidates, in the second step we built a curated dataset comprising the top \minedprojects repositories. Examples of projects in this dataset include \textsc{React}, \textsc{Node JS}, and \textsc{AngularJS}. Table~\ref{tab:projects-statistics} presents some statistics about the projects we consider in our research. The size of the projects range from small ones (5543 lines of code) to complex systems with more than 1 MLOC. All projects in our dataset have at least \num{1244} forks and \num{23672} stars. We automated all the steps to filter, clone, and collect the statistics from the repositories using Python scripts.

>>>>

\begin{enumerate}[(RQ1)]
\item \rqa 
\item \rqb
\item \rqc  
\item \rqd
\end{enumerate}

@@

In the first study, we explore the impact of atom candidates on
understanding JavaScript code (goal of research question RQ1).	
To this end, we investigate whether or not code snippets that
contain atom candidates (a) produce a higher
misunderstanding rate when programmers
try to predict their outcome and (b) require
programmers to take longer to predict their output.
Since JavaScript and C have some constructs in common (Section~\ref{sec:aoc}), we first selected a set of atoms of confusion for the \clang language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} whose idioms also exist in JavaScript programs. Our supplementary material
summarizes all atoms we consider in our research.

@@

Having selected 10 atoms in our first study, we wrote small pieces of code that contained each atom. We also wrote their equivalent snippet without the confusing idioms and constructs, leading to a total of 20 code snippets. In order to reduce the cognitive effort, we decided that each subject would be asked to predict the output of a subset of 10 code snippets, wherein each subset contained five blocks of code that contained atoms of confusion, whilst the remaining five had the atoms removed. The order in which the questions were presented was randomized. By doing this, we were seeking to minimize the chances of subjects being aware that the current listing they were analyzing contained (or not) atoms of confusion.
That is, each respondent of the survey should indicate what would be the outcomes of the code snippets, some of them having atoms of confusion (while other code snippets did not). 
We measured answer correctness and the total time each participant needed to answer the survey's questions.

@@

To complement our initial survey, we performed semi-structured interviews with professional JavaScript developers, aiming to identify their perceptions regarding code snippets containing atoms of confusion (research question RQ2). We also asked each participant if they knew of any other JavaScript-specific construct that they regarded as being likely to make the code hard to understand (research question RQ3). In this section we detail the protocol we followed to conduct the interviews and to analyze the results.

@@

In the second part of the interview our aim was to allow the subjects to describe
their JavaScript experience, as well as to allow them to reveal any JavaScript's constructs they regarded as innately confusing. This would allow us to identify potential atom candidates that are more specific to the JavaScript language. Examples of questions we explored in this section include: \emph{Do you think JavaScript is a language that produces code that is hard to understand?} and \emph{Do you regard any particular construct or idiom of the language as
  especially confusing?}

@@

After filtering out JavaScript project candidates, in the second step we built a curated dataset comprising the top \minedprojects repositories. Examples of projects in this dataset include \textsc{React}, \textsc{Node JS}, and \textsc{AngularJS}. Table~\ref{tab:projects-statistics} presents some statistics about the projects we consider in our research. The size of the projects range from small ones (5543 lines of code) to complex systems with more than 1 MLOC. All projects in our dataset have at least \num{1244} forks and at least \num{23672} stars. We automated all the steps to filter, clone, and collect the statistics from the repositories using Python scripts.

### 2021-04-08 4_Result.tex
ajustes nas issues apontadas por Marcio

Our first study investigates the impact of atoms of confusion while developers try to understand JavaScript code.
We estimate this impact considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{cognitive effort} (time necessary to provide a correct answer). We receive full answers to our survey
from 140 participants (in a total of 70 replicas).
All participants had taken at least some university course or hold a bachelor
degree or equivalent, meaning the participants have had some
level of formal education on programming.
Twenty four participants hold either a master degree (21 participants) or a doctorate degree (3 participant).

@@

Each participant in this study evaluated 10 code snippets, from which 5 were in their confusing versions, whilst the other 5 contained cleaned versions of the code snippets (i.e., without the confusing constructs and idioms). The participants should provide the expected outcomes of the code snippets. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{cognitive workload} (the time taken to answer the question). 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness. Accordingly, the version of six code snippets without atoms of confusion present at least a 15\% improvement in answer correctness. In particular, the presence of the \emph{Comma Operator} atom presents the highest impact on
misunderstanding, and  
frequently used constructs and idioms, such as \emph{Post Increment} and \emph{Omitted Curly Braces} (see Section~\ref{sec:msr-results}), also introduce high degrees of confusion.
The boxplot of Figure~\ref{fig:boxplotcorrectness} shows a nonnegligible decrease in the average number of incorrect answers when observing the cleaned version of the code snippets. Also, the sample of responses with no atoms had almost no dispersion, which signifies that the non-confusing code is easier to evaluate correctly.

@@

Two other developers implicitly touched upon the callback pattern, mentioning that it can be difficult to understand 'asynchronous' programming in JavaScript. Since what is really happening at a lower level is that the JavaScript engine creates a callback stack that is separate from the main execution stack, and that callback functions are only executed when the main execution stack is empty, the concepts of asynchronous events and callbacks are inseparable in the language, and any abstractions for callback functions, such as promises and async/await syntax only hide the pattern.

@@

We mined \minedprojects open source JavaScript repositories to understand how often atoms of confusion arise in real software. However, it was not possible to detect the atom Implicit Predicate using the mining techniques employed in this study because it depends on the semantics. As such, we were able to mine only the eight atoms listed in Table~\ref{tab:occurrences-summary}.

Similarly to previous studies~\cite{DBLP:conf/msr/GopsteinZFC18}~\cite{DBLP:journals/ese/MedeirosLAAKRG19}, which investigates the prevalence of atoms of confusion in open source \clang and \cpplang projects, we found that atoms of confusion frequently arise in JavaScript open source systems.

The 5 most frequently found atoms occur in at least 80\% of the projects.
Considering the extremes, atoms Ternary Operator was found in all repositories, while atom Comma Operator occurred only in 15\% of them (as seen in Table~\ref{tab:occurrences-summary}).

@@

Considering all JavaScript projects in our dataset, we found 
a total of \num{204229} atoms of confusion, though three atoms are responsible for 87.97\% of this total: Ternary Operator, Omitted Curly Braces and the Post Increment. The remaining atoms accounts for \num{24558} (12.03\%) of the total number of occurrences, and the Comma Operator and Arithmetic as Logic are the atoms that arise less frequently (0.001\% in total with 232 and 165 occurrences, respectively).

Regarding frequency, we proceeded with a classification of atom occurrences according to the metrics established by a previous study~\cite{DBLP:journals/ese/MedeirosLAAKRG19}. As such, we found 3 atoms as highly used (37.50\%), 3 as commonly used (37.50\%) and 2 atoms as little used (25.00\%). We also calculated the frequency of each atom per KLOC and found atom Ternary Operator as the most occurring in practice (10.16 occurrences per KLOC).
%In our dataset of JavaScript projects, 
%We found the Ternary Operator atom occurring more frequently than the Omitted Curly Braces, differently from what has been reported in a previous work~\cite{DBLP:conf/msr/GopsteinZFC18}. %

The results of our survey and interviews suggest that the Ternary Operator does not contribute significantly as a source of misunderstanding (increasing the number of wrong answers in 9\% of the cases, according to our survey). Nonetheless, the Post Increment Expression and Omitted Curly Braces atoms are listed in the top three sources of misunderstanding 
(see Table~\ref{tab:difference-correctness}). As such, fixing the the Post Increment and Omitted Curly Braces might solve most of the unclear code caused by atoms of confusion.

>>>>

Our first study investigates the impact of atoms of confusion while developers try to understand JavaScript code.
We estimate this impact considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{cognitive effort} (time necessary to provide a correct answer). We receive full answers to our survey
from 140 participants (in a total of 70 replicas).
All participants had taken at least some university course or hold a bachelor
degree or equivalent, meaning the participants have had some
level of formal education on programming.
Twenty four participants hold either a master degree (21 participants) or a doctorate degree
(three participants).

@@

Each participant in this study evaluated 10 code snippets, from which five were in their confusing versions, whilst the other five contained cleaned versions of the code snippets (i.e., without the confusing constructs and idioms). The participants should provide the expected outcomes of the code snippets. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{cognitive workload} (the time taken to answer the question). 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness.

Considering Table~\ref{tab:difference-correctness}, the version of six code snippets without atoms of confusion present at least a 15\% improvement in answer correctness. In particular, the presence of the \emph{Comma Operator} atom presents the highest impact on
misunderstanding, and  
frequently used constructs and idioms, such as \emph{Post Increment} and \emph{Omitted Curly Braces} (see Section~\ref{sec:msr-results}), also introduce high degrees of confusion.
The boxplot of Figure~\ref{fig:boxplotcorrectness} shows a nonnegligible decrease in the average number of incorrect answers when observing the cleaned version of the code snippets. Also, the sample of responses with no atoms had almost no dispersion, which supports the
argument that the non-confusing versions of the code snippets are
easier to evaluate correctly.

@@

Two other developers implicitly touched upon the callback pattern, mentioning that it can be difficult to understand \emph{asynchronous} programming in JavaScript. Since what is really happening at a lower level is that the JavaScript engine creates a callback stack that is separate from the main execution stack, and that callback functions are only executed when the main execution stack is empty, the concepts of asynchronous events and callbacks are inseparable in the language, and any abstractions for callback functions, such as promises and async/await syntax only hide the pattern.

@@

We mined \minedprojects open source JavaScript repositories to understand how often atoms of confusion arise in real software. We discarded in this analysis the atom Implicit Predicate,
because writing a CodeQL query for mining this particular atom is everything but trival.
As such, in this study
we only mined the eight atoms listed in Table~\ref{tab:occurrences-summary}.

Similarly to previous studies~\cite{DBLP:conf/msr/GopsteinZFC18}~\cite{DBLP:journals/ese/MedeirosLAAKRG19}, which investigates the prevalence of atoms of confusion in open source \clang and \cpplang projects, we found that atoms of confusion frequently arise in JavaScript open source systems. For instance, the 5 most frequently found atoms occur in at least 80\% of the projects.
Considering the extremes, atom Ternary Operator was found in all repositories,
while atom Comma Operator occurred in only 15\% of them (as seen in Table~\ref{tab:occurrences-summary}).

@@

Considering all JavaScript projects in our dataset, we found 
a total of \num{204229} atoms of confusion, though three atoms are responsible for 87.97\% of this total: Ternary Operator, Omitted Curly Braces and the Post Increment. The remaining atoms
account for \num{24558} (12.03\%) of the total number of occurrences, and the Comma Operator and Arithmetic as Logic are the atoms that arise less frequently (0.001\% in total with 232 and 165 occurrences, respectively).

Regarding frequency, we proceeded with a classification of \emph{atom occurrence}
according to the thresholds of a previous
study~\cite{DBLP:journals/ese/MedeirosLAAKRG19}. As such, we found three
atoms as highly used (Ternary Operator, Omitted Curly Braces, and Post Increment),
three as commonly used (Pre-Increment, Assignment as Value, and Logic as Control Flow)
and two atoms as little used (Arithmetic as Logic and Comma Operator).
We also calculated the frequency of each atom per KLOC and found the atom
Ternary Operator as the most occurring in practice (10.16 occurrences per KLOC).
%In our dataset of JavaScript projects, 
%We found the Ternary Operator atom occurring more frequently than the Omitted Curly Braces, differently from what has been reported in a previous work~\cite{DBLP:conf/msr/GopsteinZFC18}. %

The results of our survey and interviews suggest that the Ternary Operator does not contribute significantly as a source of misunderstanding (increasing the number of wrong answers in 9\% of the cases, according to our survey). Nonetheless, the Post Increment Expression and Omitted Curly Braces atoms are listed in the top three sources of misunderstanding 
(see Table~\ref{tab:difference-correctness}). As such, fixing the the Post Increment and Omitted Curly Braces might solve most of the unclear code caused by atoms of confusion
in JavaScript projects.

### 2021-04-08 5_Threats.tex
ajustes nas issues apontadas por Marcio

Since our research was conducted online with unknown participants, and thus we had no way of confirming their
levels of education and experience. Also,  we did not have a way to prevent respondents from cheating,
such as running the code on an interpreter, or consulting other people. This presents a threat to the validity to the
conclusions of our work, even though we leverage some means to try to mitigate this threat (as discussed
in Section~\ref{method}).

Another threat to our results lies in the fact that some constructs
might not be frequent, or present at all, in JavaScript code bases.
The atom candidates Arithmetic as Logic and
the Comma Operator were rarely found in the
open source JavaScript code we mined in our
third study.

A potential problem with our method is that
there little incentive for subjects to think
thoroughly about the questions. We observed a lack of
engagement when we ran the survey with undergraduate students during
a pilot study. Although our final subjects were voluntarily
partaking in the survey, we could not be sure that, after some
time taking the survey, respondents would become tired and stop thinking
clearly about the code.

Finally, in one of the atoms, namely the Omitted Curly Braces,
we intentionally removed indentation from the original code,
which is highly unusual, given that many programmers use automatic
formatting in their code editors. This can introduce some level
of artificiality to this atom's question. Nonetheless,
we discovered that JavaScript does allow the programmer
to omit the curly braces after \textit{if} statements,
and insert multiple statements in the following line.
This fact itself might constitute
a source of confusion, which we leave to analyse
in our future endeavors.

>>>>

%% Since our research was conducted online with unknown participants, and thus we had no way of confirming their
%% levels of education and experience. Also,  we did not have a way to prevent respondents from cheating,
%% such as running the code on an interpreter, or consulting other people. This presents a threat to the validity to the
%% conclusions of our work, even though we leverage some means to try to mitigate this threat (as discussed
%% in Section~\ref{method}).

%% Another threat to our results lies in the fact that some constructs
%% might not be frequent, or present at all, in JavaScript code bases.
%% The atom candidates Arithmetic as Logic and
%% the Comma Operator were rarely found in the
%% open source JavaScript code we mined in our
%% third study.

%% A potential problem with our method is that
%% there little incentive for subjects to think
%% thoroughly about the questions. We observed a lack of
%% engagement when we ran the survey with undergraduate students during
%% a pilot study. Although our final subjects were voluntarily
%% partaking in the survey, we could not be sure that, after some
%% time taking the survey, respondents would become tired and stop thinking
%% clearly about the code.

%% Finally, in one of the atoms, namely the Omitted Curly Braces,
%% we intentionally removed indentation from the original code,
%% which is highly unusual, given that many programmers use automatic
%% formatting in their code editors. This can introduce some level
%% of artificiality to this atom's question. Nonetheless,
%% we discovered that JavaScript does allow the programmer
%% to omit the curly braces after \textit{if} statements,
%% and insert multiple statements in the following line.
%% This fact itself might constitute
%% a source of confusion, which we leave to analyse
%% in our future endeavors.

### 2021-04-08 discussion.tex
ajustes nas issues apontadas por Marcio

Our work leads to several implications.
First, we generalize the
work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17},
which investigates
the impact of atom candidates on
understanding \clang and \cpplang code. That is,
similarly to their work, the atom candidates
Comma Operator, Post/Pre Increment, Omitted Curly Braces,
Assignment as Value, Implicit Predicate, Logic as
Control Flow, and Ternary Operator make the 
JavaScript code hard to understand. Our results also 
refute the hypothesis that Arithmetic as Logic is an atom of
confusion (i.e., a source of misunderstanding).
We just find some differences in the effect size
of the atom candidates, in comparison to the original
work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}.

The results of the interview study complement the understanding of atoms of confusion because the participants make clear the existence of a tradeoff between code comprehension and other quality attributes. For instance, most of the participants prefer the versions of the code with the Ternary Operator, even though they agree that its uses might contribute to the misunderstanding of JavaScript code, particularly when novices are maintaining the codebase. The participants of the interview study also mentioned other possible sources of misunderstanding in JavaScript,
including the use of prototype-inheritance and nested call-backs (as discussed in Section~\ref{sec:interview-results}). Other JavaScript atom candidates include
Object Destructuring, Array Spread, Object Spread, and Type Conversion. We conducted a non-exact replication of the three studies (survey, interview, and mining software repositories) considering these more specific JavaScript atom candidates. We confirmed that they truly correspond to sources of misunderstanding. Due to lack of space,
we cannot present all the results here, and we postpone the presentation of these results as future work.

>>>>

Our work leads to several implications.
First, we generalize the
work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17},
which investigates
the impact of atom candidates on
understanding \clang and \cpplang code. That is,
similarly to their work, the atom candidates
Comma Operator, Post/Pre Increment, Omitted Curly Braces,
Assignment as Value, Implicit Predicate, Logic as
Control Flow, and Ternary Operator make the 
JavaScript code hard to understand. Our results also 
refute the hypothesis that Arithmetic as Logic is an atom of
confusion (i.e., a source of misunderstanding).
In comparison to the previous work, our study
led to some differences in the effect size
of the atom candidates, in comparison to the original
work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}.
Altogether, we answer our first research question
\emph{\rqa}:

\begin{mh}
  {\bf Answer to RQ1:} The first study (survey) give evidence that
  the atom candidates for \clang and \cpplang
  that also exist for JavaScript correspond to
  a source of misunderstanding in
  JavaScript code. 
\end{mh}

The results of the interview study complement the understanding
of atoms of confusion because the participants make
clear the existence of a trade-off between code comprehension
and other quality attributes. For instance, most of the participants
prefer the version of the code with the Ternary Operator,
even though they agree that its uses might contribute to the
misunderstanding of JavaScript code, particularly when novices are maintaining
the codebase. The participants of the interview study also
mentioned other possible sources of misunderstanding in JavaScript,
including the use of prototype-inheritance and nested call-backs (as discussed in Section~\ref{sec:interview-results}). Other JavaScript atom candidates include
Object Destructuring, Array Spread, Object Spread, and Type Conversion.
In summary, the results of the second study (interviews) allow
us to answer the second (\rqb) and third research questions
(\emph{\rqc}).

\begin{mh}
  {\bf Answer to RQ2:} The qualitative analysis of the
  interviews supports the results of the first study,
  indicating that atoms of confusion compromise
  source code understanding. 
\end{mh}

\begin{mh}
  {\bf Answer to RQ3:} The qualitative analysis of the
  interviews suggest that specific constructs of
  JavaScript might also correspond to atoms of
  confusion, including prototype inheritance and
  nested callbacks. 
\end{mh}

The result of the third study (mining open source
Java script repositories) give evidence that,
although atoms of confusion compromise program
comprehension, they frequently appear in open
source JavaScript projects. In particular,
{\color{red}six, out of nine atoms considered
  in our study,} appear in more than 50\% of
the projects. To sum up, the third study
allows us to answer the fourth research
question (\emph{\rqd}).

\begin{mh}
  {\bf Answer to RQ4:} The MSR study reveals that
  the atoms of confusion explored in our research
  appear frequently in practice. 
\end{mh}

%% We conducted a non-exact replication of the three
%% studies (survey, interview, and mining software repositories)
%% considering these more specific JavaScript atom candidates.
%% We confirmed that they truly correspond to sources of misunderstanding.
%% Due to lack of space,
%% we cannot present all the results here, and we postpone the presentation of these results as future work.

### 2021-04-08 main.tex
inclusao da secao de discussao
revisao inicial da secao de ameacas
ajustes nas issues apontadas por Marcio

\documentclass[10pt,conference]{IEEEtran}

@@

@@

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

@@

\input{1_Introduction}
\input{2_Background}
\input{3_Method}
\input{4_Result}
\input{5_Threats}
\input{6_Conclusion}
% \input{7_Atoms}

\section*{Acknowledgment}

\section*{References}
\bibliographystyle{IEEEtran}
\bibliography{reference}

>>>>

\documentclass[10pt,conference,blind]{IEEEtran}

@@

\newcommand{\rqa}{What is the impact of atoms of confusion on the comprehension of
  JavaScript code?}

\newcommand{\rqb}{Do JavaScript developers identify atoms of confusion as contributing to program misunderstanding?}

\newcommand{\rqc}{What are the particular JavaScript idioms and language constructs that might cause source code misunderstanding?}

\newcommand{\rqd}{What is the frequency of occurrence of atoms of confusion in practice (i.e., in open-source JavaScript projects)?}

@@

\author{\IEEEauthorblockN{Anonymous}}

%% \author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
%% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID}
%% \and
%% \IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID}
%% \and
%% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
%% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID}
%% \and
%% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
%% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID}
%% \and
%% \IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
%% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID}
%% \and
%% \IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%% \textit{name of organization (of Aff.)}\\
%% City, Country \\
%% email address or ORCID}
%% }

@@

\input{1_Introduction}
\input{2_Background}
\input{3_Method}
\input{4_Result}
\input{discussion}
\input{5_Threats}
\input{6_Conclusion}
% \input{7_Atoms}

% \section*{Acknowledgment}

\bibliographystyle{IEEEtran}
\bibliography{reference}
